Exploration of empirical Bayes hierarchical modeling for the analysis of genome-wide association study data

### 2017-06-25 doc/manuscript/paper.tex
Activate inference using 0 contact counts with PO

Let us first introduce some notations. Hi-C data can be summarized as an $n
\times n$ contact count matrix, where each row and column corresponds to a
genomic window or loci, and each entry $c_{ij}$ refers to the number of time
$i$ and $j$ have been seen interacting with one another.

Hi-C data suffers from technical and biological biases that need to be
corrected. We use ICE

@@

A crucial step of our analysis of the \em{P. falciparum} genome relied on
visual introspection of a consensus 3D model of the genome. Being able to
quickly visualize how chromosome folded, where families of genes lied in the
3D space or whether regions where enriched helped us integrate with other
sources of data.

Briefly, we cast the problem of finding a consensus 3D structure $X \in R^{n
\times n}$ as an optimization problem, where we attempted to place each beads
in 3D so that they match as closely sa possible a predefined
``wish-distance``. We added constraints to our model based on prior knowledge,
such as the size of the nucleus, or how far apart two adjacent beads should
lie, though we showed these constraints where well satisfied even when
performing an unconstrained optimized. In this section, I will review the
inference method we used in \citet{ay:three-dimensional} as well as two newer
methods, based on well-grounded statistical method.

@@

\begin{equation}
\end{equation}

>>>>

Let us first introduce some notations. Hi-C data can be summarized as an $n
\times n$ symmetric contact count matrix, where each row and column corresponds to a
genomic window (or loci), and each entry $c_{ij}$ refers to the number of time
$i$ and $j$ have been seen interacting with one another. The matrix is hollow

Hi-C data suffers from technical and biological biases that need to be
corrected. \fixme{blha}

@@

A crucial step of our analysis of the \textit{P. falciparum} genome relied on
visual introspection of a consensus 3D model of the genome. Being able to
quickly visualize how chromosome folded, where families of genes lied in the
3D space or whether regions where enriched helped us integrate with other
sources of data.

Briefly, we cast the problem of finding a consensus 3D structure $X \in R^{n
\times n}$ as an optimization problem, either as minimizing a cost function,
(often measuring the error between euclidean distance of $\mathbf{X}$ and a
series of ``wish distances'') or maximizing a likelihood. The optimization
problem can either be unconstrained or constrained to reflect some prior
knowledge on the structure (size and shape of the nucleas, distances between
loci, etc).

 We added constraints to our model based on prior knowledge,
such as the size of the nucleus, or how far apart two adjacent beads should
lie, though we showed these constraints where well satisfied even when
performing an unconstrained optimized. In this section, I will review the
inference method we used in \citet{ay:three-dimensional} as well as two newer
methods, based on well-grounded statistical method.

@@

\begin{equation}\label{eq:mds1} 
\renewcommand{\arraystretch}{2} 
\begin{array}{ccll} 
\underset{\mathbf{X}}{\text{minimize}} & & 
\underset{(i,j) \in \mathcal{D}}{\sum} w_{ij} \big(d_{ij}(\mathbf{X}) - \delta_{ij}\big)^2
\,,&\\ 
\end{array} 
\end{equation}

where $w_{ij}$ corresponds to weight.
